Topology and experimental distinguishability

### 2017-08-07 Articles/TopologyAndExperimentalDistinguishability/article.tex
Using Mark's wording

\begin{proof}
	We need to show that the basis-to-basis topology is a topology. By definition, it is closed under finite intersection and arbitrary union. The set $V(X,\emptyset)$ is in the topology and contains no functions.  The set $V(X,Y)$ is in the topology and contains all functions.
\end{proof}

>>>>

\begin{proof}
	The collection $\mathsf{T}(C(X,Y), \mathcal{B}_X, \mathcal{B}_Y)$ is defined to be the topology generated by the sets $V(U_X,U_Y)$, so it contains the empty set, all of $C(X,Y)$, and is closed under arbitrary union and finite intersection by definition.
\end{proof}
